### 2019-10-11 Manuscript/manuscript.tex
add Penokean details to text and add to tectonic summary

Crustal growth also progressed at this time in the Paleoproterozoic through accretionary orogenesis. This accretion occurred within the Wopmay orogen through ca. 1.88 Ga arc-continent collision that led to the accretion of the Hottah terrane (the Calderian orogeny) and the subsequent emplacement of the Great Bear magmatic zone from ca. 1.88 to 1.84 Ga \citep{Hildebrand2009a}. Coeval with the Trans-Hudson orogeny was the perphiral Penokean orogeny on the southern margin of the Superior province with the last evidence of that orogeny being ca. 1.78 undeformed plutons of the East Central Minnesota Batholith \citep{Holm2005a}.

@@

\begin{figure}
\centering
\includegraphics[width=4in]{../Figures/Tectonic_history.pdf}
\caption{\small{\textbf{Simplified summary of Laurentia's tectonic history over the past $\sim$1.8 billion years.} Brief summaries and references related to the orogenic and rifting episodes are given in the text. Note that the Penokean orogeny overlaps with the Trans-Hudson orogeny and is not shown.}}
\label{fig:tectonic_history}
\end{figure}

>>>>

Crustal growth also progressed at this time in the Paleoproterozoic through accretionary orogenesis. This accretion occurred within the Wopmay orogen through ca. 1.88 Ga arc-continent collision that led to the accretion of the Hottah terrane (the Calderian orogeny) and the subsequent emplacement of the Great Bear magmatic zone from ca. 1.88 to 1.84 Ga \citep{Hildebrand2009a}. Coeval with the Trans-Hudson orogeny was the perphiral Penokean orogeny during which both microcontinent blocks (the Marshfield terrane) and arc terranes accreted on the southeastern margin of the west Superior province ca. 1.86 to 1.82 \cite{Schulz2007a}. Firm evidence of the end of the orogeny comes from the ca. 1.78 undeformed plutons of the post-Penokean East Central Minnesota Batholith \citep{Holm2005a}.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../Figures/Tectonic_history.pdf}
\caption{\small{\textbf{Simplified timeline of Laurentia's tectonic history over the past $\sim$1.8 billion years.} Brief summaries and references related to the orogenic and rifting episodes are given in the text. A timeline of large igneous provinces  (LIPs) associated with typically brief and voluminous (or interpreted to be voluminous) volcanism is also shown. The interpreted age of paleomagnetic poles for Laurentia (not included separated terranes) compiled in this study for the Proterozoic and in \cite{Torsvik2012a} for the Phanerozoic is shown.}}
\label{fig:tectonic_history}
\end{figure}
